Indirect elicitation as a necessary condition for consistent surrogate losses

### 2020-05-29 neurips-20/cvx-flats.tex
flavor text at beginning of Sec 3

\section{Consistency implies indirect elicitation}\label{sec:consis-implies-indir}
While the subtleties of \emph{consistency} vary slightly within the literature, we use two definitions that have the same implications, but one may be more appropriate than the other in a given context.

\begin{definition}[Consistent: loss]\label{def:consistent-ell}
	A loss and link $(L,\psi)$ are consistent with respect to an original loss $\ell$ if, for all distributions $D$ over input and label spaces $\X \times\Y$, and for all sequences of measurable hypothesis functions $\{f_m : \X \to \R\}$,
	\begin{align*}
	\E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X), Y) &\implies \E_D \ell((\psi \circ f_m)(X), Y) \to \inf_f \E_D \ell((\psi \circ f)(X), Y)~.~
	\end{align*}
\end{definition}
\bo{I guess we need the inf to be over a certain class of functions...the left and right side expectations need to be well-defined.}

For continuous properties, such as the expected value, variance, and entropy, asking for a consistent surrogate with respect to an original \emph{loss} may not make sense when we do not have one.
In this setting, we also define consistency with respect to a property that one wishes to estimate.

@@

	The $p$-weighted Minkowski sum $\oplus_y p_y \partial L(u,y) = \{p_1 x_1 + \ldots + p_n x_n : x_1 \in \partial L(u,1), \ldots, x_n \in \partial L(u,n) \}$.
	In order for $\vec 0$ to be in this $p$-weighted Minkowski sum, we then have that each choice of $x_i$ is a flat for $\partial L(u, i)$.
	Moreover, with $p$ fixed, we know there is a vector of witnesses $W = [x_1, \ldots, x_n] \in \reals^{d\times n}$ such that $\sum_y p_y x_y = \vec 0$; $W$ is similar to $\mathbf{A}^m$ in the proof of~\cite[Theorem 16]{ramaswamy2016convex}.
	With $W' := [W;\ones^T]$, we can now take $F := \ker(W') = \{x \in \affhull(\simplex) : W' x = \vec 0\}$, whose codimension is at most $d + 1$.
	We particularly have $p \in F$ by construction.

>>>>

\section{Consistency implies indirect elicitation}\label{sec:consis-implies-indir}
%While the subtleties of \emph{consistency} vary slightly within the literature, we use two definitions that have the same implications, but one may be more appropriate than the other in a given context.
\bo{This will need some references!}
\paragraph{Background.}
A basic requirement of surrogate losses $L$ is \emph{consistency}, which roughly means that minimizing $L$-loss corresponds to solving the original problem of interest.
We can show a learning problem is hard by showing that consistency is not possible without a certain amount of complexity -- here, dimensionality $d$ of the prediction space.
But consistency, which we formalize below, is not very tractable, so we seek more useful necessary conditions.
Ideally, such a condition would apply to all of the following settings:
\begin{itemize}
  \item The original prediction space is either discrete, e.g. a classification problem; or it is continuous, e.g. a regression or estimation problem.
  \item The original prediction problem is given either directly by a loss $\ell$, for which $L$ should be a surrogate; or it is given by a \emph{property} or statistic that we would like to estimate, for example the mean, variance, or entropy of the conditional distributions $D_x$.
\end{itemize}
In particular, a highly-studied case consists of discrete prediction spaces along with original losses $\ell$, for example, surrogates for $0-1$ loss.
Here a notable more-tractable condition is \emph{calibration}, which has been used to prove lower bounds on dimension of consistent surrogates.\bo{references, etc}
An example is the \emph{feasible subspace dimension} approach of \bo{TODO}.

\paragraph{Our approach: indirect elicitation.}
In this section, we show that indirect elicitation gives a single necessary condition for consistency that applies to all of the above settings.
This criterion is implied by both consistency and calibration (as fully explored in Appendix \bo{TODO}), so it might be viewed as a weak necessary condition for existence of a dimension-$d$ surrogate.
Yet it gives state-of-the-art lower bounds on $d$.
In particular, indirect-elicitation bounds imply feasible subspace dimension bounds.

To begin, we formalize consistency in two ways.
First (Definition \ref{def:consistent-ell}), if one is given an original loss $\ell$, then we say $L$ is consistent if optimizing $L$ implies optimizing $\ell$.
Second (Definition \ref{def:consistent-prop}), if one is given a property $\gamma$ (for example, the conditional mean), then we say $L$ is consistent if optimizing $L$ implies approaching, in some measurable sense, the correct statistic $\gamma(D_x)$ of the conditional distributions.
We will then show that consistency always implies $L$ indirectly elicits $\prop{\ell}$ or $\gamma$ respectively.

\begin{definition}[Consistent: loss]\label{def:consistent-ell}
	A loss and link $(L,\psi)$ are consistent with respect to an original loss $\ell$ if, for all distributions $D$ over input and label spaces $\X \times\Y$, and for all sequences of measurable hypothesis functions $\{f_m : \X \to \R\}$,
	\begin{align*}
	\E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X), Y) &\implies \E_D \ell((\psi \circ f_m)(X), Y) \to \inf_f \E_D \ell((\psi \circ f)(X), Y)~.~
	\end{align*}
\end{definition}
\bo{On the right side, is measurable enough? I guess we need $\psi \circ f$ to be measurable...on the other hand, we don't want to constrain $f$ based on $\psi$. Do we need a condition on $\psi$ that guarantees $\psi \circ f$ is measurable?}

In an estimation task, rather than being given an original loss $\ell$, one may be given a property such as the expected value, variance, or entropy.
In this case, we formalize consistency as converging to the correct conditional estimates of the property.
Convergence is measured by functions $\propdis(r, p)$ that formalize how close $r$ is to ``correct'' for conditional distribution $p$, i.e. in particular we should have $\propdis(r,p) = 0 \iff r \in \gamma(p)$.

@@

	The $p$-weighted Minkowski sum $\oplus_y p_y \partial L(u,y) = \{p_1 x_1 + \ldots + p_n x_n : x_1 \in \partial L(u,1), \ldots, x_n \in \partial L(u,n) \}$.
	In order for $\vec 0$ to be in this $p$-weighted Minkowski sum, we then have that each choice of $x_i$ is a flat for $\partial L(u, i)$.
	Moreover, with $p$ fixed, we know there is a vector of witnesses $W = [x_1, \ldots, x_n] \in \reals^{d\times n}$ such that $\sum_y p_y x_y = \vec 0$.
	With $W' := [W;\ones^T]$, we can now take $F := \ker(W') = \{x \in \affhull(\simplex) : W' x = \vec 0\}$, whose codimension is at most $d + 1$.
	We particularly have $p \in F$ by construction.
